### 2019-04-03 papers/journal/conclusion.tex
Updated conclusion

\noindent 
%
We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
%
\todo{Copied! Need revision}In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
%
With this tool, we made an attempt to present multiple new testable predictions. 
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.

>>>>

\noindent 
%
\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
%
For example, are there any k-connected graphs that can not be annotated into a VTS? 
%
This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
%
We are planning to use QBF(quantified Boolean
formulas) solvers or develop iterative search algorithm for such queries.
%
One may be interested in counting the number of graphs that satisfy a given
property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are also planning to employ some methods for approximate counting
of solutions.

We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
%
\todo{Copied till para end! Need revision}In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
%
With this tool, we made an attempt to present multiple new testable predictions. 
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.
